Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
non-local -> nonlocal

\begin{document}
    \title{Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tfraser@perimeterinstitute.ca}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with a particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the nonclassical nature of the causal structure in a device-independent fashion. In structures where all parties share a common resource, these nonclassical correlations are also known as non-local correlations. Any constraint satisfied by all correlations which are classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure (E. Wolfe \textit{et al.}, \href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}) in the form of polynomial inequalities, begging the question of whether any of those inequalities admit violation by quantum correlations. Numerical investigation suggests that they do not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of causal compatibility inequalities for the Triangle structure which do admit quantum violation. This provides a robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed nonclassical. Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure markedly lacks causal influence from one party to another. In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are nonclassical yet are attainable via local measurements on a shared quantum resource.

@@

    Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example. The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics. The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}. Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tfraser@perimeterinstitute.ca}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with a particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the nonclassical nature of the causal structure in a device-independent fashion. In structures where all parties share a common resource, these nonclassical correlations are also known as nonlocal correlations. Any constraint satisfied by all correlations which are classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently derived for the Triangle structure (E. Wolfe \textit{et al.}, \href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}) in the form of polynomial inequalities, begging the question of whether any of those inequalities admit violation by quantum correlations. Numerical investigation suggests that they do not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of causal compatibility inequalities for the Triangle structure which do admit quantum violation. This provides a robust-to-noise witness of quantum correlations in the Triangle structure. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed nonclassical. Often, distributions incompatible with the Bell structure are referred to as nonlocal because the Bell structure markedly lacks causal influence from one party to another. In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are nonclassical yet are attainable via local measurements on a shared quantum resource.

@@

    Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example. The phenomenology associated with Bell nonlocality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics. The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}. Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:
